rough outline

### 2022-04-29 population_data.Rmd
A little clean up
New population data set

high_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(Year)

@@

low_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia'))%>% 
  group_by(Year)

@@

joined_country_pop <- full_join(country_deaths, edit, by = c("country" = "Country.Name"))
```

>>>>

high_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Nigeria', 'Germany', 'Pakistan', 'Australia')) %>% 
  group_by(Year)

@@

low_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('Canada', 'Chile', 'Malawi', 'Serbia', 'Sri Lanka', 'New Zealand'))%>% 
  group_by(Year)

@@

joined_country_pop <- full_join(country_deaths, edit, by = c("country" = "Country.Name"))

#ggplot(joined_df, aes(fill=Count, y=country, x=year)) + 
#  geom_bar(position="stack", stat="identity")

#pops_by_country$Country.Name[[Indicator.Name("Population, total" >= 130000000)]
#rownames(table_name)[rownames(table_name) == "old label"] = "new label"
```
